Application of large language models to a geographical analysis of business practices: a case of law firms naming in Russia

### 2024-09-05 law-firms-names/Paper.Rmd
Add data and code availability statement, #4

**Keywords:** firm names; law firms; text embeddings; economic regions, text similarity.

@@

# Code availability

>>>>

**Keywords:** firm names; law firms; text embeddings; economic regions, text similarity; large language models.

@@

A dataset about Russian law firms, vectors of law firm names obtained from Yandex Foundation models, results of manual labelling, additional files used for mapping, as well as all the code used to conduct the study and generate the paper file are available at Zenodo: https://doi.org/10.5281/zenodo.13691418.
